Capital Budget Funding in Toronto

### 2024-09-25 paper/paper.qmd
began draft of abstract and introduction

---
title: "Capital Budget Allocations and Median Household Income "
subtitle: "My subtitle if needed"
author: 
  - Maria Mangru 
thanks: "Code and data are available at: https://github.com/MariaMangru/Capital-Budget-Allocations-and-Median-Household-Income."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
```

@@

You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.

The remainder of this paper is structured as follows. @sec-data....

@@

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

@@

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

Talk way more about it.

# Results

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

# Discussion

>>>>

---
title: "Capital Budget Funding in Toronto"
subtitle: "An Analysis of the Funding Disparties Across Toronto Wards (2022 - 2031)"
author: 
  - Maria Mangru 
thanks: "Code and data are available at: https://github.com/MariaMangru/Capital-Budget-Allocations-and-Median-Household-Income."
date: today
date-format: long
abstract: "This research examines the allocation of capital funding across Toronto's 25 wards and explores how these allocations correspond with various socioeconomic indicators. The analysis reveals significant disparities in per capita funding, with higher-income wards often receiving more funding than lower-income wards."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

Toronto, often referred to as a cultural mosaic, is home to a diverse population with roots from all around the world. It is also city where its neighbourhoods vary significantly in income, educational attainment, and demographic makeup. The allocation of capital funding plays an important role in shaping the infrastructure and services available to residents. This impacts their quality of life and access to opportunities.

Despite the importance of equitable funding, there is evidence that budget distributions may not align with the needs of different communities. \[Write about these two:https://www.ncbi.nlm.nih.gov/pmc/articles/PMC8186789/ , http://neighbourhoodchange.ca/documents/2016/05/walks-etal-2016-income-inequality-toronto-york-rp-238.pdf\]

By analyzing data from the City of Toronto's Capital Budget & Plan, as well as its Ward Profiles, this research finds disparities in per capita funding among the 25 wards. The findings indicate that higher-income wards tend to receive more funding per capita than lower-income wards.

The remainder of the paper is organized as follows: Section \ref{sec-data} describes the data sources and methodology used in the analysis. Section \ref{sec-results} presents the results, highlighting key findings. Section \ref{sec-discussion} discussed the implications of the findings as well as limitations and recommendations for next steps.

@@

@@

# Results {#sec-results}

@@

# Discussion {#sec-discussion}
